---
title: "Untitled"
format: html
editor: visual
bibliography: references.bib
params:
  my_class: "suv"
---

```{r}
#| label: setup

library(tidyverse)

smaller <- diamonds |> 
  filter(carat < 2.5)
```

## Quarto

Today we are working through the use of Quarto to create documents to communicate the findings generated with data science.

How to quote:

[@marmont2022]

italics and boldened ***This guy is full of crap***

how to hyperlink [R 4 Data Science 2e](https://r4ds.hadley.nz/quarto.html)

Overview of formatting options:

## header

*italic*

**bold**

***bold and italic***

~~strike~~

`code`

superscript^2^

subscript~2~

# header1

## header2

### header3

#### header4

##### header5

###### header6

List formatting: - bulleted list

-   second item

-   second item level 2

1.  numbered list
2.  numbered list
3.  numbered list level 2

# url

<https://r4ds.hadley.nz/quarto.html>

# image insertion


# table insertion

| x   | y   |
|-----|-----|
| a   | 1   |
| b   | 2   |

STOP: Insert a footnote, pagebreak, and quote with the visual insert tool then look into the source editor to see how to achieve it manually.

[^1]

[^1]: this is a footnote

------------------------------------------------------------------------

> This is a quote

Continuing ctrl + alt + I is the shortcut for a code chunk

```{r}
# this is a comment in our code
```

```{r}
#| label: simple-addition

1 + 1

# you can manually enter a code chunk by typing the backticks and curly braces
```

```{r}
#| label: chunk_options
#| eval: true
#| include: false
#| echo: false
#| results: false
#| fig-show: hide
#| error: false
```

To set global chunk options do it in the YAML under execute like: execute: echo: false error: false

`r nrow(diamonds)`

We know that there are `r nrow(diamonds)` observations in the data set and we know that there are `r nrow(diamonds) - nrow(smaller)` diamonds that are bigger than 2.5 carats

```{r}
mtcars
```


```{r}
mpg |> 
  filter(class == params$my_class) |> 
  ggplot(aes(x = displ, y = hwy)) +
    geom_point()
```
